---
title: "Project_IST 687"
author: "Ruchak V, Vinit H, Chaitra C, Chaitanya C, Shourya G"
date: "02/12/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Importing libraries
```{r}
library(tidyverse)
```

Reading the data
```{r}
hotelData <- read_csv("https://intro-datascience.s3.us-east-2.amazonaws.com/Resort01.csv")
```

Descriptive Statistics
```{r}
str(hotelData)
```

```{r}
summary(hotelData)
```

Visualizing and checking for missing values
```{r}
hotelData$Country[hotelData$Country=="NULL"] <- NA
#Converting "NULL" in Country to NA
hotelData  %>%
  summarise_all(list(~is.na(.)))%>%
  pivot_longer(everything(),
               names_to = "columns", values_to="missing") %>%
  count(columns, missing) %>%
  ggplot(aes(y=columns,x=n,fill=missing))+
  geom_col()
```

Analyzing the columns
```{r}
hist(hotelData$LeadTime)
```
```{r}
hist(hotelData$IsCanceled, breaks = 2)
```

```{r}
hist(hotelData$StaysInWeekendNights)
```
Boxplots of numerical variables against the isCanceled attribute

```{r}
boxplot(LeadTime ~ IsCanceled, data = hotelData)
```
Checking Patterns
```{r}
library(ggplot2)
ggplot(data = hotelData, aes(x = MarketSegment, y = LeadTime, color=IsCanceled)) +
  geom_bar(stat = "identity") 
  #labs(x = "zipcode")

ggplot(data = hotelData, aes(x = MarketSegment)) +
  geom_bar()
```
```{r}
hotelData$IsCanceled<-as.factor(hotelData$IsCanceled)
ggplot(data = hotelData, aes(x = DepositType, y = LeadTime, color=IsCanceled)) +
  geom_bar(stat = "identity")  
  #labs(x = "zipcode")

ggplot(data = hotelData, aes(x = DepositType)) +
  geom_bar()
```

```
Maps
```{r}
?joinCountryData2Map
joinData <- joinCountryData2Map( hotelData,
                                 joinCode = "ISO3",
                                 nameJoinColumn = "Country")

theMap <- mapCountryData( joinData, nameColumnToPlot="LeadTime", addLegend=FALSE )
do.call( addMapLegend, c(theMap, legendWidth=1, legendMar = 2))
```
