---
title: "Project 687"
author: "Ruchak V, Vinit H, Chaitra C, Chaitanya C, Shourya G"
date: "18/11/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
library(tidyverse)
```

```{r}
hotelData <- read_csv("https://intro-datascience.s3.us-east-2.amazonaws.com/Resort01.csv")
```

```{r}
str(hotelData)
```

```{r}
summary(hotelData)
```

Converting required columns to categorical factor types
```{r}
hotelData$IsCanceled <- as.factor(hotelData$IsCanceled)
hotelData$Meal <- as.factor(hotelData$Meal)
hotelData$Country <- as.factor(hotelData$Country)
hotelData$MarketSegment <- as.factor(hotelData$MarketSegment)
hotelData$IsRepeatedGuest <- as.factor(hotelData$IsRepeatedGuest)
hotelData$ReservedRoomType <- as.factor(hotelData$ReservedRoomType)
hotelData$AssignedRoomType <- as.factor(hotelData$AssignedRoomType)
hotelData$DepositType <- as.factor(hotelData$DepositType)
hotelData$CustomerType <- as.factor(hotelData$CustomerType)
```

```{r}
str(hotelData)
```

Checking for NA in columns
```{r}
sum(is.na(hotelData$LeadTime))
sum(is.na(hotelData$StaysInWeekendNights))
sum(is.na(hotelData$StaysInWeekNights))
sum(is.na(hotelData$Adults))
sum(is.na(hotelData$Children))
sum(is.na(hotelData$Babies))
sum(is.na(hotelData$PreviousCancellations))
sum(is.na(hotelData$PreviousBookingsNotCanceled))
sum(is.na(hotelData$BookingChanges))
sum(is.na(hotelData$RequiredCarParkingSpaces))
sum(is.na(hotelData$TotalOfSpecialRequests))
#We can see that all the columns are clean
```
Producing tables of categorical variables

```{r}
table(hotelData$IsCanceled)
```

```{r}
table(hotelData$Meal)
```

```{r}
table(hotelData$Country)
```

```{r}
table(hotelData$MarketSegment)
```

```{r}
table(hotelData$IsRepeatedGuest)
```

```{r}
table(hotelData$ReservedRoomType)
```

```{r}
table(hotelData$AssignedRoomType)
```

```{r}
table(hotelData$DepositType)
```

```{r}
table(hotelData$CustomerType)
```

Plotting using ggplot2

```{r}
#install.packages("ggplot2")
library(ggplot2)
```


Linear models
```{r}
#install.packages("caret")
library(caret)
#install.packages("kernlab")
library(kernlab)
```

```{r}
set.seed(1)
trainList <- createDataPartition(y=hotelData$IsCanceled, p=0.66, list=FALSE)
#creating a trainList of only the IsCanceled column with a partition at the 66%
#mark of the dataset
#str(trainList)
trainSet <- hotelData[trainList,]
#creating a training dataset of xyz records
testSet <- hotelData[-trainList,]
#creating a testing dataset of  xyzrecords
```
```{r}
dim(trainSet) 
#verifying that the training dataset has 26441 records
```
```{r}
dim(testSet)
#verifying that the testing dataset has 13619 records
```
```{r}
modelSVM1 <- ksvm(IsCanceled ~ LeadTime, data=trainSet, C = 5, cross = 3, 
                 prob.model = TRUE)
```

```{r}
modelSVM1
```
```{r}
predSVM1 <- predict(modelSVM1, newdata=testSet)
```

```{r}
str(predSVM1)
```

```{r}
confMatrix <- confusionMatrix(predSVM1, testSet$IsCanceled)
confMatrix
#IsCanceled and LeadTime gives accuracy of 0.7299
```

```{r}
modelSVM2 <- ksvm(IsCanceled ~ ., data=trainSet, C = 5, cross = 3, 
                 prob.model = TRUE)
```

```{r}
modelSVM2
```

```{r}
predSVM2 <- predict(modelSVM2, newdata=testSet)
```

```{r}
str(predSVM2)
```

```{r}
confMatrix <- confusionMatrix(predSVM2, testSet$IsCanceled)
confMatrix
```
```{r}
modelSVM3 <- ksvm(IsCanceled ~ RequiredCarParkingSpaces, data=trainSet, C = 5, cross = 3, 
                 prob.model = TRUE)
```

```{r}
modelSVM3
```

```{r}
predSVM3 <- predict(modelSVM3, newdata=testSet)
```

```{r}
str(predSVM3)
```

```{r}
confMatrix <- confusionMatrix(predSVM3, testSet$IsCanceled)
confMatrix
```
```{r}
modelSVM4 <- ksvm(IsCanceled ~ MarketSegment, data=trainSet, C = 5, cross = 3, 
                 prob.model = TRUE)
```

```{r}
modelSVM4
```

```{r}
predSVM4 <- predict(modelSVM4, newdata=testSet)
```

```{r}
str(predSVM4)
```

```{r}
confMatrix <- confusionMatrix(predSVM4, testSet$IsCanceled)
confMatrix
```

```{r}
modelSVM5 <- ksvm(IsCanceled ~ DepositType, data=trainSet, C = 5, cross = 3, 
                 prob.model = TRUE)
```

```{r}
modelSVM5
```

```{r}
predSVM5 <- predict(modelSVM5, newdata=testSet)
```

```{r}
str(predSVM5)
```

```{r}
confMatrix <- confusionMatrix(predSVM5, testSet$IsCanceled)
confMatrix
```


```{r}
library(rpart)
#install.packages("e1071")
library(e1071)
```
LeadTime + StaysInWeekendNights + 
                               Country + IsRepeatedGuest + PreviousCancellations
                               + PreviousBookingsNotCanceled + BookingChanges 
                               + DepositType + CustomerType 
                               + TotalOfSpecialRequests
```{r}
cartTree <- rpart(IsCanceled ~ ., data = trainSet)
```

```{r}
#install.packages("rpart.plot")
library(rpart.plot)
rpart.plot(cartTree)
```
```{r}
library(tidyverse)
varImp <- varImp(cartTree)
arrange(varImp, desc(Overall))
```

```{r}

```



```{r}
cartTree <- rpart(IsCanceled ~ ., data = trainSet)
#creating a rpart model and saving it in a variable called cartTree
#the outcome variable is credit_risk and the rest of the attributes are the 
#predictors
#prp(cartTree, faclen = 0, cex = 0.8, extra = 1)
#prp is used to visualize the model 
```

```{r}
#install.packages("rpart.plot")
library(rpart.plot)
rpart.plot(cartTree)
#visualize the model using rpart.plot()
```


```{r}
rpartPred <- predict(cartTree, newdata=testSet, type="class")
#rpartPred stores the prediction of cartTree by using predict() on the testing 
#dataset
confusionMatrix(rpartPred, testSet$IsCanceled)
#using the caret package to create a confusion matrix
#the accuracy of this model is 0.6941 and the NIR is 0.7
#we can see that the p-value is not lesser than 0.05 and hence we can say
#that the model may not be that good.
```

```{r}
varImp(cartTree)
#we can see that amount and duration are the most important importance. 
#The attribute 'age' is an inappropriate attribute as it is not fair to judge if
#a person will be reliable borrowers or not on the basis of age. 
#We would address this situation by removing this attribute and rerun the 
#analysis
```

Association rule mining

```{r}
#install.packages("arules")
library(arules)
#install.packages("arulesViz")
library(arulesViz)
```

```{r}
hotelDataTransactions <- as(hotelData, 'transactions')
rules1 <- apriori(hotelDataTransactions,
                  parameter=list(supp=0.1, conf=0.55),
                  control=list(verbose=F),
                  appearance=list(default="lhs",rhs=("IsCanceled=1")))
inspect(rules1)
```



```{r}
rules2 <- apriori(hotelDataTransactions,
                  parameter=list(supp=0.08, conf=0.55),
                  control=list(verbose=F),
                  appearance=list(default="lhs",rhs=("IsCanceled=0")))
inspect(rules2)
```

Inspecting maps using country data
```{r}
#install.packages("rworldmap")
library(rworldmap)
```

```{r}
?joinCountryData2Map
joinData <- joinCountryData2Map( hotelData,
                                 joinCode = "ISO3",
                                 nameJoinColumn = "Country")

theMap <- mapCountryData( joinData, nameColumnToPlot="IsCanceled", addLegend=FALSE )
do.call( addMapLegend, c(theMap, legendWidth=1, legendMar = 2))
```

```{r}
theMap <- mapCountryData( joinData, nameColumnToPlot="LeadTime", addLegend=FALSE )
do.call( addMapLegend, c(theMap, legendWidth=1, legendMar = 2))
```
```{r}
theMap <- mapCountryData( joinData, nameColumnToPlot="DepositType", addLegend=FALSE )
do.call( addMapLegend, c(theMap, legendWidth=1, legendMar = 2))
```

